Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
commas for clarity

Building on the massively parallelizable \gls{MOOSE} framework allows Moltres
to run on super-computing platforms like the Blue Waters supercomputer at the 
\gls{NCSA}. For some
three-dimensional simulations, the number of
elements in the mesh and total number of degrees of freedom exceed one million
and ten million respectively. To handle problems of this size, Moltres has been
run on up to 608 cores. However, reducing the problem dimension from three to
two and using a structured mesh that can be much more coarse in the axial
direction allows the problem to be solved on a single core in under
five minutes.

>>>>

Building on the massively parallelizable \gls{MOOSE} framework allows Moltres
to run on super-computing platforms like the Blue Waters supercomputer at the 
\gls{NCSA}. For some
three-dimensional simulations, the number of
elements in the mesh and total number of degrees of freedom exceed one million
and ten million respectively. To handle problems of this size, we ran Moltres
on up to 608 cores. However, reducing the problem dimension from three to
two and using a structured mesh, which can be much more coarse in the axial
direction, allows the problem to be solved on a single core in under
five minutes.
